---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 10,
  fig.retina = 3
)
```

# ggsegMars

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegMars/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ggsegverse/ggsegMars/actions/workflows/R-CMD-check.yaml)
[![r-universe](https://ggseg.r-universe.dev/badges/ggsegMars)](https://ggseg.r-universe.dev/ggsegMars)
<!-- badges: end -->

MarsAtlas cortical and subcortical parcellation for the ggseg ecosystem.

## Installation

We recommend installing the ggseg-atlases through the ggseg
[r-universe](https://ggseg.r-universe.dev/ui#builds):

```{r}
#| label: install-r-universe
#| eval: false
options(repos = c(
  ggseg = "https://ggseg.r-universe.dev",
  CRAN = "https://cloud.r-project.org"
))

install.packages("ggsegMars")
```

You can install this package from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("ggsegverse/ggsegMars")
```

## Cortical atlas

```{r}
#| label: cortical
library(ggseg)
library(ggsegMars)
library(ggplot2)

ggplot() +
  geom_brain(
    atlas = marsatlas_cortical(),
    mapping = aes(fill = label),
    position = position_brain(hemi ~ view),
    show.legend = FALSE
  ) +
  scale_fill_manual(values = marsatlas_cortical()$palette, na.value = "grey") +
  theme_void()
```

## Subcortical atlas

```{r}
#| label: subcortical
ggplot() +
  geom_brain(
    atlas = marsatlas_subcortical(),
    mapping = aes(fill = label),
    position = position_brain(. ~ view),
    show.legend = FALSE
  ) +
  scale_fill_manual(values = marsatlas_subcortical()$palette, na.value = "grey") +
  theme_void()
```

## Data source

Auzias G, Coulon O, Brovelli A (2016). MarsAtlas: A cortical parcellation
atlas for functional mapping. *Human Brain Mapping*, 37(4), 1573-1592.
